XXXXX \todo{Le titre !} XXXXX

### 2013-03-14 parts/def-ph.tex
proof

\subsection{The Process Hitting framework}
\label{ssec:PH}

@@

\subsection{Definition of the Process Hitting with $k$ priorities}
\towrite{Reformuler (actuellement trop proche de CMSB)}
A PH (\pref{def:PH}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.

@@

\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie}
  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities, where:
  $$\restriction{\PH}{n} = (\PHs; \PHl; \PHa^{\langle n \rangle})$$
  and:
  $$\PHa^{\langle n \rangle} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
\end{definition}

@@

@@

\subsection{Restrictions} \towrite{Reformuler}

@@

Let $\PH$ be a PH model on which we want to apply the static analysis. This PH has to regard the two restrictions below.

@@

>>>>

\section{The Process Hitting framework}

@@

\subsection{Definition of the Process Hitting with $k$ priorities}
\label{ssec:PH}
\towrite{Reformuler (actuellement trop proche de CMSB)}
A PH (\pref{def:PH}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.

@@

\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities, where:
  $$\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$$
  and:
  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$

  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
\end{definition}

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(2,0)}{b}{2}{r}
    \TSort{(4,0)}{c}{2}{r}

    \THit{a_1}{prio}{b_1}{.west}{b_0}
    \THit{b_1}{}{c_0}{.north west}{c_1}

    \path[bounce, bend right]
    \TBounce{b_1}{}{b_0}{.north west}
    ;
    \path[bounce, bend left]
    \TBounce{c_0}{}{c_1}{.south west}
    ;
  \end{tikzpicture}
  \label{fig:ph-conca}
  \caption{A simple PH example depicting “backward concurrency” between two actions belonging to different classes of priorities.}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(2,0)}{b}{2}{r}
    \TSort{(4,0)}{c}{3}{r}

    \THit{a_1}{}{b_0}{.west}{b_1}
    \THit{b_0}{prio}{c_1}{.south west}{c_0}
    \THit{b_1}{prio}{c_1}{.west}{c_2}

    \path[bounce, bend left]
    \TBounce{b_0}{}{b_1}{.south west}
    \TBounce{c_1}{}{c_2}{.south west}
    ;
    \path[bounce, bend right]
    \TBounce{c_1}{}{c_0}{.north west}
    ;
  \end{tikzpicture}
  \label{fig:ph-concb}
  \caption{A simple PH example depicting “forward concurrency” between two actions belonging to different classes of priorities.}
\end{figure}

@@

\subsection{Hypothesis} \towrite{Reformuler}

@@

Let $\PH$ be a PH model on which we want to apply the static analysis.

We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
\begin{align*}
\PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{\prio(b)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_n)) = a \\
  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
\end{align*}

We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ as :
$$
\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}
$$

We define the neighbor actions of any sort $a$ as :
$$
\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}
$$

This PH has to regard the two following restrictions.

@@

These restrictions bring new interesting properties to the PH models regarding them.

\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired. Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
\begin{theorem}
\label{th:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}

\begin{proof}
  Because of the cycle-freeness of $\restriction{\PH}{k-1}$, $\restriction{\PH}{\prio(a)}$ is also cycle-free and there is a $\delta \in \Sce$ so that $\forall h' \in \PHh$, $h'$ cannot be played in $s \PHplay \delta$. Furthermore, $\forall h' \in \delta, \PHsort(\PHtarget(h')) \neq a$ by construction of $\Vs(a)$.
\end{proof}

\begin{corollary}
  \label{co:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $(\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \forall h' \in \delta_n, \PHsort(\PHtarget(h')) \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
\end{corollary}

\pref{th:totalss} states that from any state, a steady state is eventually reached. A local variant of this theorem, given in \pref{co:totalss}, can be derived,
where, for all $\Omega \subset \PHs$, $$\restriction{\PHl}{\Omega} = \underset{a \in \Omega}{\times} \PHl_a$$ and
for all $H \subset \PHh$, $$\restriction{\Sce}{H} = \{ \delta \in \Sce \mid \forall n \in \indexes{\delta}, \delta_n \in H \} \enspace .$$
\begin{theorem}
\label{th:totalss}
  $\forall s \in \PHl, \exists \delta \in \Sce$, no action can be played in $s \PHplay \delta$.
\end{theorem}

\begin{corollary}
\label{co:totalss}
  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{V(a)}, \exists \delta \in \restriction{\Sce}{V(a)}$, no action can be played in $s \PHplay \delta$.
\end{corollary}

\pref{th:autohits} states that any sequence $\zeta$ of self-actions can be played eventually.
\begin{theorem}
\label{th:autohits}
  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS(a)$, with $n = |\indexes{\zeta}|$ so that $\forall i \in \segm{1}{n}, \PHsort(\PHhitter(\zeta_i)) = a$.
  %If no action can be played in $V(a)$ in state $s$, then
  $\exists (\delta_i)_{i \in \segm{1}{n}} \in \Sce$ so that $\forall i \in \segm{1}{n}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$. 
\end{theorem}

\begin{proof}
  With \pref{co:vplay} applied iteratively.
\end{proof}

\towrite{Théorème nécessaire pour la suite: une séquence d'actions dans $\BS(a)$ peut être jouée si précédée ou entrelacée par des $\zeta$ (?)}

### 2013-03-14 parts/sa.tex
remove procs
proof

\newcommand{\abstr}[1]{#1^\wedge}%\text{\textasciicircum}}
\def\BS{\mathbf{BS}}
\def\prio{\mathbf{prio}}

Séquences de bonds abstraites :
$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
where $\zeta^\wedge = (\zeta^\wedge_A, \zeta^\wedge_B, \zeta^\wedge_{max})$ with:
\begin{itemize}
  \item $\zeta^\wedge_A = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$ : ens. des requis d'autres sortes (frappeurs)
  \item $\zeta^\wedge_B = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \} \cup \{ \PHtarget(\zeta_n) \mid n \in \indexes{\zeta} \}$ : ens. des processus nécessaires (à ne pas perturber)
  \item $\zeta^\wedge_{max} = \max_{n \in \indexes{\zeta}}(\prio(\zeta_n))$ : plus faible priorité
\end{itemize}

Voisinage :
\begin{equation*}
\begin{split}
    V: \wp(\PHproc) \times \segm{1}{k} &\rightarrow \wp(\PHh) \\
    (ps; m) &\mapsto \sfp{\PHh^{(m)+}_{cibles}(ps)}{hs}{\PHh^{(m)+)}_{bonds}(\widehat{B}(hs)) \cup hs)}
  \end{split}
\end{equation*}
where:
\begin{equation*}
\begin{split}
    \widehat{B}: \wp(\PHh) &\rightarrow \wp(\PHproc) \\
    hs &\mapsto \{ \PHhitter(h) \mid h \in hs \} \cup \{ \PHtarget(h) \mid h \in hs \}
  \end{split}
\end{equation*}
\begin{equation*}
\begin{split}
    \PHh^{(m)+}_{\mathsf{ref}}: \wp(\PHproc) &\rightarrow \wp(\PHh) \quad,\quad m \in \segm{0}{k} \text{ and } \mathsf{ref} \in \{ \PHhitter, \PHtarget, \PHbounce \} \\
    ps &\mapsto \{ h \in \PHh \mid \mathsf{ref}(h) \in ps \wedge \prio(h) \leq m \}
  \end{split}
\end{equation*}

>>>>

Approximation : pour qu'une séquence de bonds soit jouable, il faut pouvoir atteindre tous les processus nécessaires depuis tous les points fixes possibles locaux, uniquement à l'aide d'actions de priorité maximale pour la sorte considérée.

%%% N'est plus utile (?)
%Plus haute priorité :
%$$\forall a \in \PHs, \priomax(a) = \max_{h \in \PHh, \PHtarget(h) = a}(\prio(h))$$

%%% N'est plus utile (?)
%Processus possibles :
%\begin{align*}
%\procs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
%\\ & \vee p = \PHtarget(P)
%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
%%\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
%\end{align*}

Processus rencontrés :
\begin{align*}
\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
\\ & \vee p = \PHtarget(P)
%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
\end{align*}

\subsection{Local fixed points}

%%% Pas utile
%Points fixes possibles : pour toute sorte $a$ et tout contexte partiel $\ctx$ sur $V^n(a)$:
%\begin{align*}
%  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
%  a &\mapsto \{ s \in \underset{b \in V^n(a)}{\times} \PHl_b \mid \text{$s$ est accessible depuis $\ctx$ et aucune action n'y est jouable} \}
%\end{align*}

\towrite{Formaliser}

Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
\begin{align*}
  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
  a &\mapsto \{ s \in \restriction{\PHl}{\Vs(a)} \mid \text{$s$ est (localement) accessible dans $\restriction{\PH}{\prio(a)}$ depuis $\ctx$}\\
  &\qquad\qquad\qquad\qquad \text{et aucune action n'y est jouable} \}
\end{align*}

Processus rencontrés comme résultats d'un point fixe :
\begin{align*}
\pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
\end{align*}

%%% N'est plus adapté
%Points fixes possibles sur un ensemble de sortes :
%\begin{align*}
%  \pfp: \mathbb{A} &\rightarrow \wp(\PHproc) \\
%  \myB &\mapsto \bigcup_{a \in A} \pfp_{\allprocs(\myB)}(a)
%\end{align*}

\begin{comment}
Séquences de bonds abstraites :
$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
where $\zeta^\wedge = (\zeta^\wedge_A, \zeta^\wedge_B, \zeta^\wedge_{max})$ with:
\begin{itemize}
  \item $\zeta^\wedge_A = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$ : ens. des requis d'autres sortes (frappeurs)
  \item $\zeta^\wedge_B = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \} \cup \{ \PHtarget(\zeta_n) \mid n \in \indexes{\zeta} \}$ : ens. des processus nécessaires (à ne pas perturber)
  \item $\zeta^\wedge_{max} = \max_{n \in \indexes{\zeta}}(\prio(\zeta_n))$ : plus faible priorité
\end{itemize}
\end{comment}

\subsection{Abstract structure}
%Séquences de bonds abstraites :
%$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
%where:
%$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$

\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\Proc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $
  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
  $,
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \exists (Q, P) \in \myreq \cup \mysat \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
      & \qquad\qquad a_j \neq a_k \wedge a_j \in \pfpprocs_\ctx(a) \\
      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

\def\muconcr{\ell}
\def\uconcr{\muconcr_\ctx}

\begin{theorem}[Approximation inf.]\label{th:approxinf}
If the graph $\cwB$ contains no cycle and all objectives have at least one solution, then $\uconcr(\w) \neq \emptyset$.
\end{theorem}

\begin{proof}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$ and
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.

\begin{itemize}
  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$,
    or $\forall \zeta \in \BS(P), \zeta \in \Sce \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$ and $\delta$ is given by \pref{th:autohits}.

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists Q \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \pfp_{s_n}(a)$.
          If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
          By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \Sce$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
          \todo{Il reste à montrer que $\delta'_n$ ne perturbe pas $b$. Ça se montre par contradiction grâce à l'hyopthèse de cycle-freeness.}
          .
%        \item[*] For $n \in \segm{1}{m-1}$, $m = |\indexes{\zeta}|$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_n \PHplay \delta'_n \PHplay \zeta_n$ and $\zeta_{n+1} = \PHhit{c_i}{a_j}{a_k}$.
%          By hypothesis, $\exists \delta_1 \in \muconcr_{s_n}(\PHobj{\any}{c_i}), \PHget{s_n \PHplay \delta_{n+1}}{a} \in \pfp_s(a)$.
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
\end{proof}

\begin{comment}
Voisinage :
\begin{equation*}
\begin{split}
    V: \wp(\PHproc) \times \segm{1}{k} &\rightarrow \wp(\PHh) \\
    (ps; m) &\mapsto \sfp{\PHh^{(m)+}_{cibles}(ps)}{hs}{\PHh^{(m)+)}_{bonds}(\widehat{B}(hs)) \cup hs)}
  \end{split}
\end{equation*}
where:
\begin{equation*}
\begin{split}
    \widehat{B}: \wp(\PHh) &\rightarrow \wp(\PHproc) \\
    hs &\mapsto \{ \PHhitter(h) \mid h \in hs \} \cup \{ \PHtarget(h) \mid h \in hs \}
  \end{split}
\end{equation*}
\begin{equation*}
\begin{split}
    \PHh^{(m)+}_{\mathsf{ref}}: \wp(\PHproc) &\rightarrow \wp(\PHh) \quad,\quad m \in \segm{0}{k} \text{ and } \mathsf{ref} \in \{ \PHhitter, \PHtarget, \PHbounce \} \\
    ps &\mapsto \{ h \in \PHh \mid \mathsf{ref}(h) \in ps \wedge \prio(h) \leq m \}
  \end{split}
\end{equation*}
\end{comment}

\begin{figure}
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,right of=c01] (c01s) {};
    \node[Aproc,right of=c01s] (b1) {$b_1$};
    \node[Aobj,right of=b1] (b11) {$\PHobj{b_1}{b_1}$};
    \node[Asol,right of=b11] (b11s) {};
    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Anos,right of=b01] (b01nos) {$\bottom$};

    \path
    (c1) edge (c01)
    (c01) edge (c01s)
    (c01s) edge (b1)
    (b1) edge (b11) edge (b01)
    (b11) edge (b11s)
    ;
  \end{tikzpicture}
  \label{fig:sa-conca}
  \caption{The local causality graph of the PH in \pref{fig:ph-conca}.}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c2) {$c_2$};
    \node[Aobj,right of=c2] (c12) {$\PHobj{c_1}{c_2}$};
    \node[Asol,right of=c12] (c12s) {};
    \node[Aproc,right of=c12s] (b1) {$b_1$};
    \node[Aobj,right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Asol,right of=b01] (b01s) {};
    \node[Aproc,right of=b01s] (a1) {$a_1$};
    \node[Aobj,right of=a1] (a11) {$\PHobj{a_1}{a_1}$};
    \node[Asol,right of=a11] (a11s) {};

    \node[Aobj,above right of=c2] (c22) {$\PHobj{c_2}{c_2}$};
    \node[Asol,right of=c22] (c22s) {};
    \node[Aobj,below right of=c2] (c02) {$\PHobj{c_0}{c_2}$};
    \node[Anos,right of=c02] (c02nos) {$\bottom$};

    \path
    (c2) edge (c12) edge (c22) edge (c02)
    (c22) edge (c22s)
    (c12) edge (c12s)
    (c12s) edge (b1)
    (b1) edge (b01)
    (b01) edge (b01s)
    (b01s) edge (a1)
    (a1) edge (a11)
    (a11) edge (a11s)
    ;
  \end{tikzpicture}
  \label{fig:sa-concb}
  \caption{The local causality graph of the PH in \pref{fig:ph-concb}.}
\end{figure}
